Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
explain why lazy

Recently, \citet{new2019gradual} show that \eager{} strategies are 
incompatible with $\eta$-equivalence of functions, which suggest that these 
strategies are not very ideal.

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.

\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}

>>>>

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hypercoercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) cast calculus. This is 
the first bisimulation proof for the \lazyD{} cast calculus as far as we know.
We care more about lazy strategies because recently, \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that these strategies are not very ideal. 
\todo[inline]{Explain why we care about \lazyD{} and \lazyUD{}. -Jeremy}
\todo[inline]{Explained, not sure if it suffice. -KC}
